---
title: "Create Network"
author: "Bo Werth"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Create Network}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

```{r setup, eval=FALSE, echo=FALSE}
# rmarkdown::render(file.path(dbpath, "GitHub", "networkD3", "vignettes", "createNetwork.rmd"))
```

## Naming

Choose network name according to main d3.layout function, e.g. "cluster", "chord" etc.

## R

Create R script at `\R` containing the following functions:

- `...Network`: this function calls `htmlwidgets` to create the HTML
- `...NetworkOutput`: calls `shinyWidgetOutput` for shiny integration
- `render...Network`: calls `shinyRenderWidget` for shiny integration
- `as.xxxNetwork`: convert `hclust` or dendrogram object into networkD3 list

## YAML

Create file with YAML frontmatter at `\inst\htmlwidgets`. If CSS is required, add a line e.g. `style: chordNetwork.css`

## JS

Create file with JavaScript content for `HTMLWidgets.widget()` function at `\inst\htmlwidgets`

`initialize`
:   - create svg using `d3.layout.xxx()` function  
	- replace `height` and `width` with `diameter`
	- add `scale` transformation attribute

`resize`
:   currently not working properly - should take `height` and `width` parameters to change size of existing svg 

`renderValue`
:   remove existing children and add values  
    Datatypes  
    - list (JSON.parse)
    - matrix (JSON.parse)
    - table (d3.csv.parse)

## CSS

Create file with css information at `\inst\htmlwidgets\lib\css-0`

## Examples

```{r prepare, eval = TRUE, echo = FALSE}
require(networkD3)
require(rjson)
```

```{r test, eval = FALSE, echo = FALSE}
devtools::install_github("alexcb/rjson", subdir = "rjson")
devtools::install(file.path(dbpath, "GitHub", "rjson", "rjson"))
test proper functioning of rjson "simplify":
line 12: "flare.animate.Easing": only one import, brackets dropped
"name":"flare.animate.Easing","size":17010,"imports":["flare.animate.Transition
ui.icionet.FlareImports <- file.path(dbpath, "GitHub", "networkD3", "data", "readme-flare-imports.json")
ui.icionet.FlareImports <- rjson::fromJSON(file = ui.icionet.FlareImports, simplify = FALSE)
ui.icionet.FlareImports.json <- rjson::toJSON(x = ui.icionet.FlareImports)
start <- 2482
cat('\n', substr(ui.icionet.FlareImports.json, start, (start + 78)), '\n\n')
```

### Cluster Network

```{r cluster, eval = TRUE}
## load data
data_list_path <- file.path(system.file(file.path("data", "readme-flare-imports.json"),
                                        package = "networkD3"))
data_list <- rjson::fromJSON(file = data_list_path, simplify = FALSE)

networkD3::clusterNetwork(List = data_list,
                                    height = 700, width = 700,
                                    fontSize = 10,
                                    linkColour = "#ccc",
                                    nodeColour = "#fff",
                                    nodeStroke = "steelblue",
                                    textColour = "#111",
                                    opacity = 0.9,
                                    margin = 0)

```

### Treemap Network

```{r treemap, eval = TRUE}
## load data
data_list_path <- file.path(system.file(file.path("data", "readme-flare-imports.json"),
                                        package = "networkD3"))
data_list <- rjson::fromJSON(file = data_list_path, simplify = FALSE)

networkD3::treemapNetwork(List = data_list,
                          height = 400,
                          width = 700,
                          fontSize = 10,
                          linkColour = "#ccc",
                          nodeColour = "#fff",
                          nodeStroke = "steelblue",
                          textColour = "#111",
                          opacity = 0.9,
                          margin = 0)

```

### Chord Network

```{r chord, eval = TRUE}
## load data
data.table <- read.csv(system.file(file.path("data", "cities.csv"),
                                   package = "networkD3"))
data.matrix <- JSONtoMatrix(file = system.file(file.path("data", "matrix.json"),
                                               package = "networkD3"))
rownames(data.matrix) <- NULL
colnames(data.matrix) <- NULL

networkD3::chordNetwork(matrix = data.matrix,
                        digits = 5,
                        df = data.table,
                        height = NULL,
                        width = NULL,
                        fontSize = 10,
                        linkColour = "#ccc",
                        nodeColour = "#fff",
                        nodeStroke = "steelblue",
                        textColour = "#111",
                        opacity = 0.9,
                        margin = 0)
```

```{r testing, eval = FALSE, echo = FALSE}

miserables <- system.file(file.path("data", "miserables.json"), package = "networkD3")
MisLinks <- JSONtoDF(file = miserables, array = "links")
MisNodes <- JSONtoDF(file = miserables, array = "nodes")

forceNetwork(Links = MisLinks,
             Nodes = MisNodes,
             Source = "source",
             Target = "target",
             Value = "value",
             NodeID = "name",
             Group = "group",
             opacity = 0.5
             )


Energy <- file.path(dbpath, "GitHub", "networkD3", "data", "energy.json")
EngLinks <- JSONtoDF(file = Energy, array = "links", simplify = FALSE)
EngNodes <- JSONtoDF(file = Energy, array = "nodes", simplify = FALSE)

sankeyNetwork(Links = EngLinks,
              Nodes = EngNodes,
              Source = "source",
              Target = "target",
              Value = "value",
              NodeID = "name",
              fontsize = 12,
              nodeWidth = 30,
              )

Flare <- file.path(dbpath, "GitHub", "networkD3", "data", "flare.json")
Flare <- rjson::fromJSON(file = Flare)

treeNetwork(List = Flare,
            fontSize = 10,
            opacity = 0.9,
            margin=0)

```
